The language of generalization: Probability, vagueness, and interaction

### 2018-05-31 paper/comgen-paper.Rmd
default gen discussion; unified perspective discussion; edits to discussion; fix figures to render in text; update hab endorsement figure; degens comments

Insofar as there is a single class of linguistic expressions that convey generalization, there should be something common to them all: a literal meaning that unifies generic, habitual, and causal language.
In this paper, we propose such a semantic core based on probability and formalized using the standard tools of truth-functional semantics [@Montague1973; @Cohen1999] .
A semantics based on probability is not enough, however.
We propose that the meaning of generalizations is underspecified or *vague* and that listeners derive a more precise interpretation in context.
The fact that generics are vague, however, does not preclude them from being treated with formal models.
We draw upon the tools of Bayesian models of cognition [@Tenenbaum2011] to formalize the vagueness and context-dependence of generic language [@Frank2012; @GoodmanLassiter].
By its instantiation in a formal model, this hypothesis has meaningful conditions under which it can be tested.
It is also the first theory to make quantitative predictions about human understanding of generalization in language.
<!-- With these ideas, we create an endorsement model, that describes what makes generalizations in language true or false. -->
<!-- Our model is the first to make quantitative predictions about human endorsements of generalizations in language. -->

@@

Generalizations are used to make predictions about events or properties of instances that an agent has yet to experience [@HumeTHN].
People readily predict that the next dog they encounter will have four legs, drinking another cup of coffee will cause jitters, and a new day will find people that we know doing what they habitually do. 
In each case, we assign a specific exemplar $x$ to a category $k$, and make a prediction that it will have feature $f$.
This prediction can be described by a conditional probability: $P(x \in f \mid x \in k)$, the probability that $x$ will have $f$ given that it is in $k$ (formally, an instance of $k$ will be in the set of things that have $f$), which we will refer to as the *prevalence* and for convenience write as $p = P(f \mid k)$.
Our *prevalence* $p$ is a *prevalence in the mind*, a latent sense that a future instance of a category would have a particular property; others might call this projectibility [@Goodman1955].
The targets of our predictions can vary widely: They may be objects (a dog), events (a coffee drink), or more fine-grained types (a person on a particular day).
The properties also vary (e.g., having fur, causing jitters, going to the gym).
Yet the mathematical description of the inductive belief is always given by a probability $P(f \mid k)$.

@@

If generalization from observations can be described by a probability $p$, it is natural to posit that same construct will be at the heart of a semantic theory of the language of generalization (Ingredient 1: Probability).
In semantics, belief updating generally passes through Boolean *truth values* [@Montague1973].
The simplest way to derive a Boolean from a scalar quantity like probability is via a *threshold semantics*: The utterance is true if the relevant scalar value is above a threshold.
For example, the sentence "Some dogs have four legs" is believed to be literally true if the chances that an individual dog will have four legs is more than 0%: $\denote{some}(p) = \{p > 0\}$.
"Most dogs have four legs" can also be described as a threshold on prevalence (e.g., the chances that a dog will have four legs is greater than 50%): $\denote{most}(p) = \{p > 0.5\}$.
Thus, the simplest semantics for a generalization would also be a threshold on the prevalence: $\denote{gen}(p, \theta) = \{p >\theta\}$.

The obvious next question for such a representation concerns $\theta$: What threshold is appropriate?
It has been argued that generic language is more fundamental than quantified language [e.g., "some", "most"; @Leslie2007; @Gelman2009], which can be described using particular values of $\theta$: $\denote{some}(p) = \{p > 0\}$; $\denote{most} = \{p > 0.5\}$.
In a probabilistic representation, states of uncertainty are more fundamental than states of certainty (e.g., it is a special case when an agent with probabilistic beliefs is certain about something; the more typical case is that they are uncertain). 
Thus, if quantifiers have *certain* thresholds ("some": greater than 0; "most" greater than 0.5), then perhaps generics have *uncertain* thresholds.
We formalize this underspecification of meaning (Ingredient 2: Vagueness) by putting a probability distribution over $\theta$: $P(\theta)$ [@Lassiter2013; @Lassiter2015; cf., @Qing2014].

@@

Our endorsement model (Eq. \ref{eq:S1}) provides a mapping from the prevalence in the category being referred to (i.e., how many robins lay eggs)---the *referent prevalence* $p$---to an endorsement probability for the corresponding generalization (e.g., "Robins lay eggs"): $S(u = u_{gen} \mid p)$. 
The model assumes a threshold semantics based on probability (prevalence) but does not require specifying the threshold *a priori* (note that there is no $\theta$ in the left-hand side of Eq. \ref{eq:S1}).
This formalism builds on a tradition in formal semantics to try to precisely define the conditions under which a sentence is true or false [@Montague1973].
We go beyond previous semantic models of generics [e.g., @Cohen1999] by embedding our semantic hypothesis (a simple but vague threshold) in a cognitive model in which relevant contextual knowledge can be formalized.
In this simple model, the relevant contextual knowledge is given by a prior distribution over the prevalence $P(p)$.

@@

Prior distributions over prevalence can be revealed by considering the prevalence of the feature in alternative categories.
Think about five of your favorite kinds of animal: What percentage of each of them *are female*? What percentage of each of them *lay eggs*?
Figure\ \@ref(fig:simulations) (row 1) show hypothetical prevalence priors for six different properties.
The *lay eggs* distribution has substantial probability mass near 0 (since many animal categories do not have egg-layers) with a secondary component peaked around 0.5, because among the animals with egg-layers, only the female members of the category have the property.
Conversely, the distribution over the prevalence of *being female* is unimodal and centered at 0.5, because almost all animals have female members in that proportion.

@@

The human species is remarkable not only because we can extract useful generalizations from observations of the world, but because we can convey these generalizations to each other succinctly using language.
Generalizations expressed in language (e.g., "John runs.", "Dogs are friendly.", "Fire causes smoke.") are a premier example of how simple statements---statements understood by even the youngest language users---can convey subtle meanings and display complex sensitivities to context.
We have argued that the core meaning of such linguistic expressions can be understood by a vague threshold function that operates over a speaker's inductive beliefs, formalized in terms of predictive probability or *prevalence*.
Critically, deploying this simple semantics within a formal framework for pragmatic language understanding leads to complex interactions with background knowledge.
<!--
formalize their meaning by appealing to prevalence, which we define as a predictive probability (as opposed to frequency).
As a formal theory of the language of generalization, our framework unifies large swaths of language about distinct semantic types, illustrated here with categories, events, and causes.

Generalization underlies each of these, and we formalize their meaning by appealing to prevalence, which we define as a predictive probability (as opposed to frequency).
-->
We tested this theory by exploring its implications for truth judgments, modeled as a speaker's decision about whether it would be useful to utter the generalization. 
Endorsement, we have shown, depends in systematic ways on the listener's prior beliefs about prevalence.
This framework accounts for a number of philosophically puzzling generic statements (Expt. 1), naturally extends to other domains of generalizations (habituals and causals; Expts. 2 \& 3), and provides an avenue for top-down moderators on language use by way of predictive probability (Expt. 2c).
We have provided strict tests of our formal model by both measuring and manipulating listeners' background knowledge as well as comparing our model to a number of alternatives.
In each case, our model provided a strong quantitative fit to human judgements while other models fall short.

Our model leverages the insights of truth-functional semantics and computational cognitive modeling to articulate how an agent should update their beliefs based on a generic sentence. 
The Bayesian model provides a clean separation of the semantics of a generalization (represented formally by a threshold-function) from world knowledge (represented by the prevalence prior).
Previous theoretical accounts have either aimed to account for the context-sensitivity of generics by positing distinct semantic constructs [e.g., *relative* vs *absolute* generics, described below; @Cohen1999] or positing a semantics that cannot be separated from world knowledge [@Leslie2008].
Here, we demonstrate how the context-sensitivity of generics can emerge via the interplay of a stable (but vague) semantics and diverse background knowledge.

@@

Communicating probabilities might seem contrary to the long attested failures in reasoning about probability [@Tversky1974].
Our theory suggests that the problems with understanding probabilities observed in classic, cognitive psychology paradigms are a problem in understanding explicit probabilities expressed using *numerical language*, a historically quite recent innovation [cf., @Levinson1995]. 
Rather than conveying probabilities explicitly, generalizations convey them implicitly.
In other words, we argue that the utterance "70% of birds fly" is a precise statement about how many birds fly in the way that "John is 6'3"" is a precise statement about the height of John, whereas "Birds fly" is a vague statement more akin to utterance "John is tall".
The latter statements are easier to process, understood at an earlier age, and may be more useful for human reasoning. 
Indeed, young children are actually quite good with reasoning about probabilities, but in ways that are not explicit or tied to the numerical language of probability [@Xu2008; @xu2009statistical].

@@

In the rest of this discussion, we elaborate how our model relates to language understanding more generally, sketch its application to several philosophical puzzles in genericity, and situate our theory with respect to extant theories of generic language.

@@

Our theory assumes that listeners and speakers share relevant background knowledge (at least in the form of a *prevalence prior*) against which generalizations are interpreted.
In our modeling work, we found that prevalence prior distributions were well-modeled by a mixture-model with two mixture components.
Such a prior distribution implies categorical distinctions between different kinds of categories, perhaps by virtue of having (or lacking) certain causal mechanisms that can bring about the target feature.
Actual conceptual knowledge, needed to interpret generalizations, is most likely richer than our simple two-component prevalence distributions.

Conceptual structure, including higher-order abstractions, can be formalized in probabilistic causal models [@pearl1988probabilistic; @Gopnik2003theory] and their generalization in probabilistic programs [@Goodmanconcepts].
We believe such probabilistic concept representations can be adopted as a formal analog to intuitive theories of natural kinds [@Gelman2003; @Keil1992].
We do not assume a particular view of natural kinds in our model, but note that viewing natural kinds as richly structured categories with clusters of non-obvious properties is compatible with our information-theoretic communicative model. 
The important commonality among different domain-specific background theories is that they each have a statistical aspect (supporting prediction via beliefs about prevalence), which language can interface with.
Thus, our theory provides a separation between conceptual knowledge and the semantics of generalizations; the interface between the two is predictive probability or *prevalence*.

The fact that conceptual knowledge is not a part of our formal semantics does not imply that such knowledge is peripheral to communicating with generalizations.
Not only does conceptual knowledge influence interpretation via prevalence priors, but it may very well be what the speaker intends to communicate.
Like other probabilistic pragmatic models, our model distinguishes the semantic contribution of an utterance (what enters into the truth-functional semantics) from a speaker's utility in producing that utterance. 
For simplicity, the model presented here assumes these two are the same: the speaker's utility comes from conveying prevalence. 
However, the model makes nearly identical predictions if the speaker's utility comes from communicating the abstract parameters of the prevalence distributions [e.g., if the speaker intends to convey that "K is the kind of thing that Fs"; cf., @Prasada2006].
This observation may prove useful for constructing models of teachers, whose goals include conveying abstract relations between kinds and properties.

@@

The probabilistic communicative model we introduce in this paper assumes shared background about the statistics of an event or property in question, represented by the prior belief distribution over the prevalence $P(p)$.
We constructed prevalence priors for a property, event, or cause by considering *other possible* categories having the property, people doing the action, or causes producing the effect.
In Expt. 3, we empirically demonstrated the influence of other categories on endorsement of generalizations.
Collectively, these other kinds, people, or causes form *comparison classes* against which the referent-category is evaluated.
Thus, the prevalence prior $P(p)$ is actually a conditional distribution constructed with respect some comparison class $C$: $P(p \mid C)$.

The existence of comparison classes is uncontroversial in the study of *vague* or *underspecified* language [e.g., gradable adjectives like *tall* and vague quantifiers like *many*; @Bale2011; @Solt2009].
Adult judgments of the felicity of gradable adjectives like *tall* or *dark* depend upon fine-grained details of the statistics of the comparison class [@Qing2014; @Schmidt2009; @Solt2012] in ways directly analogous to the context-sensitivity highlighted here for the language of generalizations.
An important problem for comparison classes for both gradable adjectives and generalizations is that the comparison class often goes unsaid (e.g., "John is tall for a person" is often produced as just "John is tall"; "Robins lay eggs relative to other animals" is just "Robins lay eggs").
Recent empirical and computational modeling work suggests that pragmatic reasoning combined with world knowledge can flexibly adjust the comparison class to appropriately suit the context [@Tessler2017].
In this paper, we do not include such a mechanism in our model; instead made the comparison class clear to participants in order to study the remaning context-sensitivity of generics.

@@

The comparison classes used in our case studies were constructed with respect to the category (*other animals*, *other people*, *other possible causes*).
Thus, our endorsement model assumes that the goal of communication, sometimes referred to as the *Question Under Discussion* or QUD [@roberts1996qud], was to address the question of "*what* has this feature?".
Were the QUD to be reversed (e.g., "what features does the category have?"), the comparison classes would be constructed with respect to the feature (e.g., *other features*, *other actions*, *other effects*).
It has long been noted that the same generalization can be used to address multiple QUDs [@KrifkaGenericBookFocus], and we posit that differences in interpretation are the result of multiple distinct comparison classes competing for influence.
Prosodic focus can change the interpretation: "*Lawyers* care about the law." suggests a category-wise comparison class perhaps in a pedagogical context (i.e., "Lawyers *(as opposed to doctors, firefighters, ...)* care about the law.") while "Lawyers care about *the law*" suggests a feature-wise comparison class perhaps produced by a sardonic speaker (i.e., "Lawyers care about the law *(as opposed to justice, doing what is morally right, ...)*").
Pragmatic reasoning is likely relevant here as well [cf., @Declerck1986; @Tessler2017].
In this work, we focused on category-wise comparison classes purely for methodological convenience.
Future work should investigate the factors that give rise to feature-wise interpretations of generalizations, how the relevant comparison classes are constructed, and how these inferences interact with threshold inference.

@@

Perhaps the most surprising aspect of the language of generalization is how difficult it is to formalize, given how common it is in child-directed and child-produced speech [@Gelman1998; @GelmanEtAl2004].
<!-- from a formal perspective is that generic language is far from trivial to characterize.  -->
<!-- Generalizations are common in child-directed and child-produced speech [@Gelman1998; @GelmanEtAl2004] and are believed to be central to the growth of conceptual knowledge [@Gelman2004], -->
Generics are often contrasted with quantifier language (e.g., "some", "most", "all", ...), which is, more difficult for young children to acquire [@Brandone2014; @Gelman2015], but easier to formalize.
<!-- If generics convey something about the probabilty of a feature, we would expect them to be in some way comparable to quantifier statments (e.g., "some", "most", "all", ...). -->
<!-- The extreme flexibility of generic meaning (e.g., "Birds lay eggs" vs. "Birds are female") stands in stark contrast to its early emergence in development. -->
<!-- In fact, quantified statements, whose formal meaning is much more straight-forward (e.g., "Some" means more than zero), emerge *later* in development [@Brandone2014; @Gelman2015], and are often confused for generic statements [@Leslie2012a]. -->
This asymmetry between the simplicity of the formal theory and the age of acquisition has led some to conclude that the normal tools for describing the semantics of quantified utterances (i.e., truth-functional notions) are inappropriate for generics [@Leslie2008].

Rejecting the tools of truth-functional semantics for generalizations would be throwing the baby out with the bathwater.
With some reasonable assumptions about the hypothesis space of semantic meanings, the acquisition of a threshold-based truth-functional meaning $\denote{u}(p, \theta) = \{p :p > \theta\}$ requires learning three distinct aspects of meaning: 
(1) the *dimension* being described (i.e., prevalence $p$),
(2) the *polarity* of the relation (i.e., $>$ vs. $<$), and 
(3) the value of the *threshold* (e.g., $\theta = 0$ for "some", $\theta = 0.5$ for "most").
Upon acquiring the dimension and the polarity, a rational learner should represent uncertainty over possible thresholds $\theta$.
Upon repeated cross-situational data with quantifiers, this prior could be updated towards acquiring a fixed meaning.
However, for generics, no fixed threshold is required; the language of generalization is learned once aspects (1) and (2) are understood.
Thus, under our framework, generics should not only be learned before quantifiers but also faciliate the acquisition of quantifiers.
<!-- In our model, $\theta$ is left underspecified in the semantics and is inferred in context. -->
<!-- This informal analysis predicts that a child would first acquire the language of generalizations, and from that, carve out more precise meanings for quantified language, consistent with the developmental data. -->

@@

<!-- The study of what makes generalizations true or false then reduces to a study of concepts [@carlson2009concepts] and kind--property relations [@Prasada2013]. -->

>>>>

Insofar as there is a single class of linguistic expressions that convey generalization, there should be something common to them all: a literal meaning that unifies generic, habitual, and causal language.
In this paper, we propose such a semantic core based on probability and formalized using the standard tools of truth-functional semantics [@Montague1973; @Cohen1999] .
A semantics based on probability will not be enough, however.
We propose that the meaning of generalizations is underspecified or *vague*, and that listeners derive a more precise interpretation in context using world knowledge.

The fact that generics are vague does not preclude them from being treated with formal models.
We draw upon the tools of Bayesian models of cognition [@Tenenbaum2011] to formalize the vagueness and context-dependence of generic language [@Frank2012; @GoodmanLassiter].
The Bayesian model separates the semantics of an utterance conveying a generalization from the world knowledge a listener would use to interpret the utterance, a key theoretical advancement beyond previous accounts.
<!-- By its instantiation in a formal model, this hypothesis has meaningful conditions under which it can be tested. -->
This formal model is the first of its kind to make quantitative predictions about human understanding of generalization in language.
<!-- With these ideas, we create an endorsement model, that describes what makes generalizations in language true or false. -->
<!-- Our model is the first to make quantitative predictions about human endorsements of generalizations in language. -->

@@

Generalizations are used to make predictions about events or properties of instances that an agent has yet to experience [@HumeTHN].
People readily predict that the next dog they encounter will have four legs, drinking another cup of coffee will cause jitters, and a new day will find people that we know doing what they habitually do. 
In each case, we assign a specific exemplar $x$ to a category $k$, and make a prediction that it will have feature $f$.
This prediction can be described by a conditional probability: $P(x \in f \mid x \in k)$, the probability that $x$ will have $f$ given that it is in $k$ (formally, an instance of $k$ will be in the set of things that have $f$), which we will refer to as the *prevalence* and for convenience write as $p = P(f \mid k)$.
Our *prevalence* $p$ is a *prevalence in the mind*, a latent belief that a future instance of a category would have a particular property; others might call this projectibility [@Goodman1955].
The targets of our predictions can vary widely: They may be objects (a dog), events (an instance of coffee-drinking), or more ad-hoc types (a person on a particular day).
The properties also vary (e.g., having fur, causing jitters, going to the gym).
Yet the mathematical description of the inductive belief is always given by a probability $P(f \mid k)$.

@@

If generalization from observations can be described by a probability $p$, it is natural to posit that same construct will be at the heart of a semantic theory of the language of generalization (Ingredient 1: Probability).
In semantics, belief updating generally passes through Boolean *truth values* [@Montague1973].
The simplest way to derive a Boolean from a scalar quantity like probability is via a *threshold semantics*: The utterance is true if the relevant scalar value is above a threshold.
For example, the sentence "Some dogs have four legs" is believed to be literally true if the chances that an individual dog will have four legs is more than 0%: $\denote{some}(p) := p > 0$.
"Most dogs have four legs" can also be described as a threshold on prevalence (e.g., the chances that a dog will have four legs is greater than 50%): $\denote{most}(p) := p > 0.5$.
Thus, the simplest semantics for a generalization would also be a threshold on the prevalence: $\denote{gen}(p, \theta) := p >\theta$.

The obvious next question for such a representation concerns $\theta$: What threshold is appropriate?
It has been argued that generic language is more fundamental than quantified language [e.g., "some", "most"; @Leslie2007; @Gelman2009], which can be described using particular values of $\theta$: $\denote{some}(p) := p > 0$; $\denote{most} := p > 0.5$.
In a probabilistic representation, states of uncertainty are more fundamental than states of certainty (e.g., it is a special case when an agent with probabilistic beliefs is certain about something; the more typical case is that they are uncertain). 
Thus, if quantifiers have *certain* thresholds ("some": greater than 0; "most" greater than 0.5), then perhaps generics have *uncertain* thresholds.
We formalize this underspecification of meaning (Ingredient 2: Vagueness) by putting a probability distribution over $\theta$: $P(\theta)$ [@Lassiter2013; @Lassiter2015; cf., @Qing2014].

@@

Our endorsement model (Eq. \ref{eq:S1}) provides a mapping from the prevalence in the category being referred to (i.e., how many robins lay eggs)---the *referent prevalence* $p$---to an endorsement probability for the corresponding generalization (e.g., "Robins lay eggs"): $S(u \mid p)$. 
The model assumes a threshold semantics based on probability (prevalence) but does not require specifying the threshold *a priori* (note that there is no $\theta$ in the left-hand side of Eq. \ref{eq:S1}).
This formalism builds on a tradition in formal semantics to try to precisely define the conditions under which a sentence is true or false [@Montague1973].
We go beyond previous semantic models of generics [e.g., @Cohen1999] by embedding our semantic hypothesis (a simple but vague threshold) in a cognitive model in which relevant contextual knowledge can be formalized.
In this simple model, the relevant contextual knowledge is given by a prior distribution over the prevalence $P(p)$.

@@

<!-- TELL US WHAT THEY ARE: BETA DISTRIBUTIONS./ -->

Prior distributions over prevalence can be revealed by considering the prevalence of the feature in alternative categories.
Think about five of your favorite kinds of animal: What percentage of each of them *are female*? What percentage of each of them *lay eggs*?
Figure\ \@ref(fig:simulations) (row 1) show hypothetical prevalence priors for six different properties, formalized as Beta distributions or mixtures of Beta distributions.^[
  The Beta distribution is a distribution over numbers between 0 and 1. 
  In other words, it is a probability distribution over probabilities, which is exactly how we are modeling prevalence. 
]
The *lay eggs* distribution has substantial probability mass near 0 (since many animal categories do not have egg-layers) with a secondary component peaked around 0.5, because among the animals with egg-layers, only the female members of the category have the property.
Conversely, the distribution over the prevalence of *being female* is unimodal and centered at 0.5, because almost all animals have female members in that proportion.

@@

The human species is remarkable not only because we can extract useful generalizations from observations of the world, but because we can convey these generalizations to each other succinctly using language.
Generalizations expressed in language (e.g., "John runs.", "Dogs are friendly.", "Fire causes smoke.") are a premier example of how simple statements---statements understood by even the youngest language users---can convey subtle meanings and display complex sensitivities to context.
We have argued that the core meaning of such linguistic expressions can be understood by three ingredients: Probability, vagueness, and context. 
Though generics are vague that does not preclude them from being treated by formal models. 
A vague threshold meaning operating over a speaker's inductive beliefs, formalized by predictive probability or *prevalence*, leads to complex, quantitative interactions with background knowledge.

<!--
formalize their meaning by appealing to prevalence, which we define as a predictive probability (as opposed to frequency).
As a formal theory of the language of generalization, our framework unifies large swaths of language about distinct semantic types, illustrated here with categories, events, and causes.

Generalization underlies each of these, and we formalize their meaning by appealing to prevalence, which we define as a predictive probability (as opposed to frequency).
-->

We tested this theory by exploring its implications for the simplest judgments a person could make: truth judgments.
We modeled truth judgments as a speaker's decision about whether it would be useful to utter the generalization. 
Endorsement, we have shown, depends in systematic ways on the listener's prior beliefs about prevalence.
This framework accounts for a number of philosophically puzzling generic statements (Expt. 1), naturally extends to other domains of generalizations (habituals and causals; Expts. 2 \& 3), and provides an avenue for top-down moderators on language use by way of predictive probability (Expt. 2c).
We have provided strict tests of our formal model by both measuring and manipulating listeners' background knowledge as well as comparing our model to a number of alternatives.
In each case, our model provided a strong quantitative fit to human judgements while other models fall short.

Our model leverages the insights of formal semantics and computational cognitive modeling to articulate how an agent should update their beliefs based on a generic sentence. 
The Bayesian model provides a clean separation of the semantics of a generalization (represented formally by a threshold-function) from world knowledge (represented by the prevalence prior).
Previous theoretical accounts have either aimed to account for the context-sensitivity of generics by positing distinct semantic constructs [e.g., *relative* vs *absolute* generics, described below; @Cohen1999] or positing a semantics that cannot be separated from world knowledge [@Leslie2008].
Here, we demonstrate how the context-sensitivity of generics can emerge via the interplay of a stable (but vague) semantics and diverse background knowledge.

@@

Communicating probabilities might seem contrary to the long attested failures in reasoning about probability [@Tversky1974].
Our theory suggests that the problems with understanding probabilities observed in classic, cognitive psychology paradigms are a problem in understanding explicit probabilities expressed using *numerical language*, a historically quite recent innovation [cf., @Levinson1995]. 
Rather than conveying probabilities explicitly, generalizations convey them implicitly.
In other words, we argue that the utterance "70% of birds fly" is a precise statement about how many birds fly in the way that "John is 6'3"" is a precise statement about the height of John, whereas "Birds fly" is a vague statement more akin to the utterance "John is tall".
The latter statements are easier to process, understood at an earlier age, and may be more useful for human reasoning. 
Indeed, even infants are actually quite good with reasoning about probabilities, but in ways that are not explicit or tied to the numerical language of probability [@Xu2008; @xu2009statistical].

@@

In the rest of this discussion, we elaborate how our model relates to language understanding more generally, situate our theory with respect to extant theories of generic language, and sketch applications to a few philosophical puzzles in genericity.

@@

Our theory assumes that listeners and speakers employ real-world knowledge of objects and events in order to use and interpret generalizations.
It is this real-world knowledge (presently formalized in terms of a *prevalence prior*) where issues about domain specific knowledge, interpretation of properties [@Prasada2006], over-hypotheses [@Leslie2008], and essentialism [@Gelman2003] can all play a role.
<!-- It was not our present goal to model this aspect of interlocutors' conceptual knowledge. -->
<!-- Instead,  -->
We hypothesize that all of this knowledge feeds into participants' predictions (or, judgments about prevalence).
<!-- which we model in a precise, quantitative manner. -->
Thus, we bring precision and clarity to the *output* of these cognitive processes and conceptual understanding: intuitions about prevalence.
Applying the same precision and clarity to the more abstract aspects of conceptual knowledge including property knowledge, essentialism, etc. is an important next step for this line of work. 
Probabilistic causal models [@pearl1988probabilistic; @Gopnik2003theory] and their generalization in probabilistic programs [@Goodmanconcepts] are obvious starting places to look for such a formalism for conceptual structure and higher-order abstractions.

 <!-- You bring precision and clarity to the judgments by capturing the output of the cognitive processes that generate prevalence.    But you tend to downplay or at least not emphasize that importance and sometime sounds as if you think you have an alternative view that argues against some of the other perspectives.    I think this is worth clarifying. -->

<!-- (at least in the form of a *prevalence prior*) against which generalizations are interpreted. -->
<!-- In our modeling work, we found that prevalence prior distributions were well-modeled by a mixture-model with two mixture components. -->
<!-- Such a prior distribution implies categorical distinctions between different kinds of categories, perhaps by virtue of having (or lacking) certain causal mechanisms that can bring about the target feature. -->
<!-- Actual conceptual knowledge, needed to interpret generalizations, is most likely richer than our simple two-component prevalence distributions. -->

<!-- Conceptual structure, including higher-order abstractions, can be formalized in probabilistic causal models [@pearl1988probabilistic; @Gopnik2003theory] and their generalization in probabilistic programs [@Goodmanconcepts]. -->
<!-- We believe such probabilistic concept representations can be adopted as a formal analog to intuitive theories of natural kinds and their properties [@Gelman2003; @Keil1992]. -->
<!-- We do not assume a particular view of natural kinds in our model, but note that viewing natural kinds as richly structured categories with clusters of non-obvious properties is compatible with our information-theoretic communicative model.  -->
<!-- The important commonality among different domain-specific background theories is that they each have a statistical aspect (supporting prediction via beliefs about prevalence), which language can interface with. -->
<!-- Thus, our theory provides a separation between conceptual knowledge and the semantics of generalizations; the interface between the two is predictive probability or *prevalence*.  -->

The fact that conceptual knowledge is not a part of our formal semantics does not imply that such knowledge is unrelated to communicating generalizations.
Not only does conceptual knowledge influence interpretation via beliefs about prevalence, but conceptual knowledge may very well be what the speaker intends to communicate.
Like other models in the probabilistic pragmatic tradition, our model distinguishes the relevant variables for the truth-functional semantics from those that impact the speaker's utility in producing the utterance. 
A speaker's utility comes from addressing an implicit goal of communication, sometimes referred to as the *Question Under Discussion* or QUD [@roberts1996qud].
The separation of the QUD from the literal, truth-functional denotation of the utterance is an important theoretical distinction made explicit in our formal modeling approach [@Goodman2016]. 
For simplicity, the model presented here assumes the QUD is about prevalence.
However, the model makes nearly identical predictions if the QUD concerns the abstract parameters of the prevalence distributions [e.g., if the speaker intends to convey that "K is the kind of thing that Fs"; cf., @Prasada2006], something much closer to communicating conceptual understanding.
This observation may prove useful for constructing models of teachers, whose goals include conveying abstract relations between kinds and properties.

@@

The probabilistic communicative model we introduce in this paper assumes shared background about the statistics of an event or property in question, represented by the prior belief distribution over the prevalence $P(p)$.
We constructed prevalence priors for a property, event, or cause by considering other possible categories having the property, people doing the action, or causes producing the effect.
In Expt. 3, we empirically demonstrated the influence of other categories on endorsement of generalizations.
Collectively, these other kinds, people, or causes form *comparison classes* against which the referent-category is evaluated.
Thus, the prevalence prior $P(p)$ is actually a conditional distribution constructed with respect to some comparison class $C$: $P(p \mid C)$.

In this paper, we have assumed particular values of $C$ for our three case studies (*animals*, *people*, and *possible causes*, respectively).
We think the choice of these classes is intuitive, but it is a limitation of this work that we do not derive these choices from more general information-theoretic considerations.
The problem of choosing a comparison classes, however, is not unique to the language of generalization, but is a problem for any theory of *vague* or *underspecified* language [e.g., gradable adjectives like *tall* and vague quantifiers like *many*; @Bale2011; @Solt2009; @Qing2014; @Schmidt2009; @Solt2012]. 
We have begun to explore how pragmatic reasoning and world knowledge can flexibly adjust the comparison class to appropriately suit the context [e.g., how a "short" basketball player is *short for a basketball player* while a "tall" basketball player is *tall for a person*; @Tessler2017].
It remains to be seen how such principles could operate on richly structured, hierarchical knowledge about categories and properties that would be important for interpreting generic language.

The employment of comparison classes in our model provides additional flexibility towards modeling different communicative goals.
The comparison classes used in our case studies were constructed with respect to the category (*other animals*, *other people*, *other possible causes*).
Thus, our endorsement model assumes that the QUD was "*what* has this feature?".
Any part of a sentence, however, can be brought into focus (e.g., by prosody) and turned into an answer to a QUD: "*Dogs* have four legs" (as opposed to other animals), "Dogs *have* four legs" (as opposed to eating or doing other things with four legs), "Dogs have *four* legs" (as opposed to two legs, three legs, six legs), "Dogs have four *legs*" (as opposed to other limbs/body parts), "Dogs *have four legs*" (as opposed to having other features).
It has long been noted that the same generalization can be used to address multiple QUDs [@KrifkaGenericBookFocus], and we posit that differences in interpretation are the result of multiple distinct comparison classes competing for influence.
<!-- "*Lawyers* care about the law." suggests a category-wise comparison class perhaps in a pedagogical context (i.e., "Lawyers *(as opposed to doctors, firefighters, ...)* care about the law.") while "Lawyers care about *the law*" suggests a feature-wise comparison class perhaps produced by a sardonic speaker (i.e., "Lawyers care about the law *(as opposed to justice, doing what is morally right, ...)*"). -->
Prosody provides a good cue towards resolving the comparison class, and pragmatic reasoning is likely relevant here as well [@Declerck1986; @Tessler2017].
In this work, we focused on category-wise comparison classes purely for methodological convenience.
Future work should investigate the factors that give rise to feature-wise interpretations of generalizations (e.g., "Dogs *have four legs*", as opposed to having other features), other QUDs generics can address, how the relevant comparison classes are constructed, and how these inferences interact with threshold inference.

<!-- Adult judgments of the felicity of gradable adjectives like *tall* or *dark* depend upon fine-grained details of the statistics of the comparison class [@Qing2014; @Schmidt2009; @Solt2012] in ways directly analogous to the context-sensitivity highlighted here for the language of generalizations. -->
<!-- An important problem for comparison classes for both gradable adjectives and generalizations is that the comparison class often goes unsaid (e.g., "John is tall for a person" is often produced as just "John is tall"; "Robins lay eggs relative to other animals" is just "Robins lay eggs"). -->
<!-- In this paper, we do not include such a mechanism in our model; instead made the comparison class clear to participants in order to study the remaning context-sensitivity of generics. -->

@@

@@

Perhaps the most surprising aspect of the language of generalization is how difficult it is to formalize, given how common it is in child-directed and child-produced speech [@Gelman1998; @GelmanEtAl2004].
<!-- from a formal perspective is that generic language is far from trivial to characterize.  -->
<!-- Generalizations are common in child-directed and child-produced speech [@Gelman1998; @GelmanEtAl2004] and are believed to be central to the growth of conceptual knowledge [@Gelman2004], -->
Generics are often contrasted with quantifier language (e.g., "some", "most", "all", ...), which is more difficult for young children to acquire [@Brandone2014; @Gelman2015], but easier to formalize.
<!-- If generics convey something about the probabilty of a feature, we would expect them to be in some way comparable to quantifier statments (e.g., "some", "most", "all", ...). -->
<!-- The extreme flexibility of generic meaning (e.g., "Birds lay eggs" vs. "Birds are female") stands in stark contrast to its early emergence in development. -->
<!-- In fact, quantified statements, whose formal meaning is much more straight-forward (e.g., "Some" means more than zero), emerge *later* in development [@Brandone2014; @Gelman2015], and are often confused for generic statements [@Leslie2012a]. -->
The assumed complexity of a formal theory of generics and the simplicity with which young children acquire generics has led some to conclude that the normal tools for describing the semantics of quantified utterances (e.g., a truth-functional threshold) are inappropriate for generics [@Leslie2008].

Rejecting the tools of truth-functional semantics for generalizations would be throwing the baby out with the bathwater.
With some reasonable assumptions about the hypothesis space of semantic meanings, the acquisition of a threshold-based truth-functional meaning $\denote{u}(p, \theta) := p > \theta$ requires learning three distinct aspects of meaning: 
(1) the *dimension* being described (i.e., prevalence $p$),
(2) the *polarity* of the relation (i.e., $>$ vs. $<$), and 
(3) the value of the *threshold* (e.g., $\theta = 0$ for "some", $\theta = 0.5$ for "most").
Upon acquiring the dimension and the polarity, a rational learner should represent uncertainty over possible thresholds $\theta$.
Upon repeated cross-situational data with quantifiers, this prior could be updated towards acquiring a fixed meaning.
However, for generics, no fixed threshold is required; the language of generalization is learned once aspects (1) and (2) are understood.
Thus, under our framework, generics should not only be learned before quantifiers but also facilitate the acquisition of quantifiers.
<!-- In our model, $\theta$ is left underspecified in the semantics and is inferred in context. -->
<!-- This informal analysis predicts that a child would first acquire the language of generalizations, and from that, carve out more precise meanings for quantified language, consistent with the developmental data. -->

@@

The present paper presents the first formal theory of generalization in language that generates quantitative predictions about human behavioral data. 
Our work builds on and relates to a number of extant theories of generics in both the formal semantics and psychological literatures.
The dominant approach from formal semantics tries to describe unified, objective criteria by which to establish if a generic and other generalizations are true or false (i.e., generic *truth conditions*).
These views are typically *statistical* and appeal to quantification or the statistics of the world (e.g., how many Ks have F) to define those unified, objective criteria.
Theorists in philosophy and psychology have argued that what matters for producing and understanding generics is not the statistics of the world, but to mental representations or abstract beliefs in the head (e.g., *there is something about being a K which causes it to F*).
Statistical and conceptual theories express the major contrasting views of generic language [@Carlson1995essay].^[
  We use the terms statistical and conceptual to refer to what @Carlson1995essay referred to as "inductive" and "rules and regulations" views, respectively.
]
